Modeling choices

### 2021-04-10 analysis/03_environment-repression.Rmd
Update analysis notebook to include new laws + latent human rights

  # Load big list of models
  model_df <- tar_read(model_df) %>% 
    filter(str_detect(model, "baseline") | str_detect(model, "v2csreprss"))

  # Load actual model objects
  tar_load(c(m_pts_baseline, m_pts_v2csreprss, 
             m_pts_baseline_rewb, m_pts_v2csreprss_rewb, 
             m_clphy_baseline, m_clphy_v2csreprss, 
             m_clphy_baseline_rewb, m_clphy_v2csreprss_rewb, 
             m_clpriv_baseline, m_clpriv_v2csreprss, 
             m_clpriv_baseline_rewb, m_clpriv_v2csreprss_rewb))

  # Load regression tables
  tar_load(c(models_tbl_e2a, models_tbl_e2b, models_tbl_e2c))

@@

>>>>

  # Load big list of models
  model_df <- tar_read(model_df) %>% 
    filter(str_detect(model, "baseline") | str_detect(model, "v2csreprss")) %>% 
    filter(!str_detect(model, "_train"))

  # Load actual model objects
  tar_load(c(m_pts_baseline, m_pts_v2csreprss, 
             m_pts_baseline_rewb, m_pts_v2csreprss_rewb, 
             m_clphy_baseline, m_clphy_v2csreprss, 
             m_clphy_baseline_rewb, m_clphy_v2csreprss_rewb, 
             m_clpriv_baseline, m_clpriv_v2csreprss, 
             m_clpriv_baseline_rewb, m_clpriv_v2csreprss_rewb,
             m_lhr_baseline, m_lhr_v2csreprss))

  # Load regression tables
  tar_load(c(models_tbl_e2a, models_tbl_e2b, models_tbl_e2c, models_tbl_e2d))

@@

# E~2d~: Civil society environment and latent physical integrity rights

```{r tbl-e2d}
# Build nicer column names
models_for_table_e2d <- models %>% 
  filter(outcome_var == "Latent human rights") %>% 
  mutate(explan_var = recode(explan_var, "Civil society repression" = "CS repression")) %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

# Make a named vector of original model names and nice names
model_names_tbl_e2d <- models_for_table_e2d %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e2d$model)

# Rename the columns
names(models_tbl_e2d) <- recode(names(models_tbl_e2d), !!!model_names_tbl_e2d)

modelsummary(models_tbl_e2d,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

```{r plot-coefs-e2d}
coef_plots <- models %>% 
  filter(str_detect(model, "m_lhr_v2csreprss")) %>% 
  mutate(re_fancy = case_when(
    re == "RE" ~ "Random effects models",
    re == "REWB" ~ "Random effects—within/between models"
  )) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `b_v2csreprss.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  filter(!str_detect(.variable, "between")) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

```{r plot-mfx-e2d}
mfx <- models %>% 
  filter(str_detect(model, "m_lhr_v2csreprss")) %>% 
  mutate(fx = map2(actual_model, "v2csreprss",
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

mfx %>% 
  filter(model == "m_lhr_v2csreprss") %>% 
  ggplot(aes(x = effect1__, y = estimate__)) +
  geom_ribbon(aes(ymin = lower__, ymax = upper__), alpha = 0.4, 
              fill = "#FF4136", color = NA) +
  geom_line(size = 1, color = "#FF4136") +
  labs(x = "Civil society repression\n(higher values = less repression)",
       y = "Predicted latent human rights\n(higher values = less violence)") +
  theme_ngo()
```

### 2021-04-10 analysis/03_laws-repression.Rmd
Update analysis notebook to include new laws + latent human rights

  # Load actual model objects
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_advocacy, m_pts_entry, m_pts_funding, 
             m_pts_baseline_rewb, m_pts_total_rewb, m_pts_advocacy_rewb, m_pts_entry_rewb, m_pts_funding_rewb, 
             m_clphy_baseline, m_clphy_total, m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
             m_clphy_baseline_rewb, m_clphy_total_rewb, m_clphy_advocacy_rewb, m_clphy_entry_rewb, m_clphy_funding_rewb, 
             m_clpriv_baseline, m_clpriv_total, m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
             m_clpriv_baseline_rewb, m_clpriv_total_rewb, m_clpriv_advocacy_rewb, m_clpriv_entry_rewb, m_clpriv_funding_rewb))

  # Load regression tables
  tar_load(c(models_tbl_e1a_re, models_tbl_e1a_rewb, 
             models_tbl_e1b_re, models_tbl_e1c_re))

@@

```{r clean-data}
models <- model_df %>% 
  mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
  mutate(across(c(outcome_var, explan_var, re, family), ~fct_inorder(., ordered = TRUE)))

coefs_clean <- tribble(
  ~coef, ~coef_clean,
  "b_barriers_total", "Total legal barriers",
  "b_barriers_total_lag1", "Total legal barriers (t - 1)",
  "b_advocacy", "Barriers to advocacy",
  "b_advocacy_lag1", "Barriers to advocacy (t - 1)",
  "b_entry", "Barriers to entry",
  "b_entry_lag1", "Barriers to entry (t - 1)",
  "b_funding", "Barriers to funding",
  "b_funding_lag1", "Barriers to funding (t - 1)",
  "b_barriers_total_within", "Total legal barriers (within)",
  "b_barriers_total_lag1_within", "Total legal barriers (within; t - 1)",
  "b_advocacy_within", "Barriers to advocacy (within)",
  "b_advocacy_lag1_within", "Barriers to advocacy (within; t - 1)",
  "b_entry_within", "Barriers to entry (within)",
  "b_entry_lag1_within", "Barriers to entry (within; t - 1)",
  "b_funding_within", "Barriers to funding (within)",
  "b_funding_lag1_within", "Barriers to funding (within; t - 1)"
) %>% 
  mutate(across(everything(), ~fct_inorder(., ordered = TRUE))) %>% 
  mutate(lagging = str_detect(coef, "lag1"))
```

@@

```{r plot-mfx-e1a}
plot_pts_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_pts_total", "barriers_total", "Total legal barriers",
  "m_pts_advocacy", "advocacy", "Barriers to advocacy",
  "m_pts_entry", "entry", "Barriers to entry",
  "m_pts_funding", "funding", "Barriers to funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

@@

```{r plot-mfx-e1b}
plot_clphy_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_clphy_total", "barriers_total", "Total legal barriers",
  "m_clphy_advocacy", "advocacy", "Advocacy",
  "m_clphy_entry", "entry", "Entry",
  "m_clphy_funding", "funding", "Funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

@@

```{r plot-mfx-e1c}
plot_clpriv_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_clpriv_total", "barriers_total", "Total legal barriers",
  "m_clpriv_advocacy", "advocacy", "Advocacy",
  "m_clpriv_entry", "entry", "Entry",
  "m_clpriv_funding", "funding", "Funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

@@

>>>>

  # Load actual model objects
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_total_new, 
             m_pts_advocacy, m_pts_entry, m_pts_funding, 
             m_pts_baseline_rewb, m_pts_total_rewb, 
             m_pts_advocacy_rewb, m_pts_entry_rewb, m_pts_funding_rewb, 
             m_clphy_baseline, m_clphy_total, m_clphy_total_new, 
             m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
             m_clphy_baseline_rewb, m_clphy_total_rewb, 
             m_clphy_advocacy_rewb, m_clphy_entry_rewb, m_clphy_funding_rewb, 
             m_clpriv_baseline, m_clpriv_total, m_clpriv_total_new,
             m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
             m_clpriv_baseline_rewb, m_clpriv_total_rewb, 
             m_clpriv_advocacy_rewb, m_clpriv_entry_rewb, m_clpriv_funding_rewb,
             m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
             m_lhr_advocacy, m_lhr_entry, m_lhr_funding))

  # Load regression tables
  tar_load(c(models_tbl_e1a_re, models_tbl_e1a_rewb, 
             models_tbl_e1b_re, models_tbl_e1c_re, models_tbl_e1d_re))

@@

```{r clean-data}
models <- model_df %>% 
  filter(!str_detect(model, "train")) %>% 
  mutate(actual_model = model %>% map(~eval(rlang::sym(.)))) %>% 
  mutate(across(c(outcome_var, explan_var, re, family), ~fct_inorder(., ordered = TRUE)))

coefs_clean <- tribble(
  ~coef, ~coef_clean,
  "b_barriers_total", "Total legal barriers",
  "b_barriers_total_lag1", "Total legal barriers (t - 1)",
  "b_barriers_total_new", "New legal barriers",
  "b_barriers_total_new_lag1", "New legal barriers (t - 1)",
  "b_advocacy", "Barriers to advocacy",
  "b_advocacy_lag1", "Barriers to advocacy (t - 1)",
  "b_entry", "Barriers to entry",
  "b_entry_lag1", "Barriers to entry (t - 1)",
  "b_funding", "Barriers to funding",
  "b_funding_lag1", "Barriers to funding (t - 1)",
  "b_barriers_total_within", "Total legal barriers (within)",
  "b_barriers_total_lag1_within", "Total legal barriers (within; t - 1)",
  "b_advocacy_within", "Barriers to advocacy (within)",
  "b_advocacy_lag1_within", "Barriers to advocacy (within; t - 1)",
  "b_entry_within", "Barriers to entry (within)",
  "b_entry_lag1_within", "Barriers to entry (within; t - 1)",
  "b_funding_within", "Barriers to funding (within)",
  "b_funding_lag1_within", "Barriers to funding (within; t - 1)"
) %>% 
  mutate(across(everything(), ~fct_inorder(., ordered = TRUE))) %>% 
  mutate(lagging = str_detect(coef, "lag1"))
```

@@

```{r plot-mfx-e1a}
plot_pts_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_pts_total", "barriers_total", "Total legal barriers",
  "m_pts_total_new", "barriers_total_new", "New legal barriers",
  "m_pts_advocacy", "advocacy", "Barriers to advocacy",
  "m_pts_entry", "entry", "Barriers to entry",
  "m_pts_funding", "funding", "Barriers to funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

@@

```{r plot-mfx-e1b}
plot_clphy_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_clphy_total", "barriers_total", "Total legal barriers",
  "m_clphy_total_new", "barriers_total_new", "New legal barriers",
  "m_clphy_advocacy", "advocacy", "Advocacy",
  "m_clphy_entry", "entry", "Entry",
  "m_clphy_funding", "funding", "Funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

@@

```{r plot-mfx-e1c}
plot_clpriv_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_clpriv_total", "barriers_total", "Total legal barriers",
  "m_clpriv_total_new", "barriers_total_new", "New legal barriers",
  "m_clpriv_advocacy", "advocacy", "Advocacy",
  "m_clpriv_entry", "entry", "Entry",
  "m_clpriv_funding", "funding", "Funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

@@

# E~1d~: NGO laws and latent physical integrity rights

```{r tbl-e1d-re}
models_for_table_e1d_re <- models %>% 
  filter(outcome_var == "Latent human rights", re == "RE") %>% 
  mutate(model_name = glue("{outcome_var} (t + 1)<br>({explan_var}; {re})"))

model_names_tbl_e1d_re <- models_for_table_e1d_re %>% 
  pull(model_name) %>% 
  set_names(models_for_table_e1d_re$model)

names(models_tbl_e1d_re) <- recode(names(models_tbl_e1d_re), 
                                   !!!model_names_tbl_e1d_re)

modelsummary(models_tbl_e1d_re,
             statistic = "[{conf.low}, {conf.high}]",
             coef_map = coef_list,
             gof_omit = "ELPD",
             escape = FALSE,
             notes = list("Posterior means; 95% credible intervals in brackets"))
```

```{r plot-coefs-e1d}
coef_plots <- models %>% 
  filter(str_detect(model, "lhr"), !str_detect(model, "baseline")) %>% 
  mutate(re_fancy = case_when(
    re == "RE" ~ "Random effects models",
    re == "REWB" ~ "Random effects—within/between models"
  )) %>% 
  mutate(coef_draws = map(
    actual_model, 
    ~gather_draws(model = ., `.*barriers.*|.*advocacy.*|.*entry.*|.*funding.*`, regex = TRUE))) %>% 
  select(-actual_model) %>% 
  unnest(coef_draws) %>% 
  filter(!str_detect(.variable, "between")) %>% 
  left_join(coefs_clean, by = c(".variable" = "coef"))

```{r plot-mfx-e1d}
plot_lhr_vars_lookup <- tribble(
  ~model, ~plot_var, ~plot_var_nice,
  "m_lhr_total", "barriers_total", "Total legal barriers",
  "m_lhr_total_new", "barriers_total_new", "New legal barriers",
  "m_lhr_advocacy", "advocacy", "Advocacy",
  "m_lhr_entry", "entry", "Entry",
  "m_lhr_funding", "funding", "Funding"
) %>% 
  mutate(plot_var_nice = fct_inorder(plot_var_nice, ordered = TRUE))

mfx <- models %>% 
  filter(str_detect(model, "lhr"), !str_detect(model, "rewb|baseline")) %>% 
  left_join(plot_lhr_vars_lookup, by = "model") %>% 
  mutate(fx = map2(actual_model, plot_var, 
                   ~conditional_effects(.x, effects = .y)[[1]])) %>% 
  select(-actual_model) %>% 
  unnest(fx)

mfx %>% 
  mutate(x_rounded = floor(effect1__)) %>% 
  group_by(x_rounded, plot_var_nice) %>% 
  slice(1) %>% 
  ungroup() %>% 
  ggplot(aes(x = x_rounded, y = estimate__, color = plot_var_nice)) +
  geom_line(size = 0.5, color = "grey90") +
  geom_pointrange(aes(ymin = lower__, ymax = upper__),
                  fatten = 1) +
  scale_x_continuous(breaks = 0:9) +
  scale_color_viridis_d(option = "plasma", end = 0.8) +
  guides(color = FALSE) +
  labs(x = "Count of legal barriers",
       y = "Predicted latent human rights value\n(higher values = better human rights)") +
  facet_grid(cols = vars(plot_var_nice), scales = "free_x", space = "free_x") +
  theme_ngo() +
  theme(panel.grid.major.x = element_blank())
```

### 2021-04-10 analysis/03_model-details.Rmd
Update analysis notebook to include new laws + latent human rights

  # So we do it this manual way
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_advocacy, 
             m_pts_entry, m_pts_funding, m_pts_v2csreprss, 
             m_pts_baseline_rewb, m_pts_total_rewb, m_pts_advocacy_rewb, 
             m_pts_entry_rewb, m_pts_funding_rewb, m_pts_v2csreprss_rewb, 
             m_clphy_baseline, m_clphy_total, m_clphy_advocacy, 
             m_clphy_entry, m_clphy_funding, m_clphy_v2csreprss, 
             m_clphy_baseline_rewb, m_clphy_total_rewb, m_clphy_advocacy_rewb, 
             m_clphy_entry_rewb, m_clphy_funding_rewb, m_clphy_v2csreprss_rewb, 
             m_clpriv_baseline, m_clpriv_total, m_clpriv_advocacy, 
             m_clpriv_entry, m_clpriv_funding, m_clpriv_v2csreprss, 
             m_clpriv_baseline_rewb, m_clpriv_total_rewb, m_clpriv_advocacy_rewb, 
             m_clpriv_entry_rewb, m_clpriv_funding_rewb, m_clpriv_v2csreprss_rewb))
})
```

@@

@@

model_time_e1 <- models_e1 %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
           `Random effects` = re, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`, `Random effects`)

@@

model_time_e2 <- models_e2 %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
           `Random effects` = re, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`, `Random effects`)

@@

- `R/models_pts.R` (for PTS-based models)
- `R/models_clphy.R` (for V-Dem physical violence-based models)
- `R/models_clpriv.R` (for V-Dem private civil liberties-based models)

@@

>>>>

  # So we do it this manual way
  tar_load(c(m_pts_baseline, m_pts_total, m_pts_total_new, 
             m_pts_advocacy, m_pts_entry, m_pts_funding, 
             m_pts_v2csreprss, 
             m_pts_baseline_rewb, m_pts_total_rewb, 
             m_pts_advocacy_rewb, m_pts_entry_rewb, m_pts_funding_rewb, 
             m_pts_v2csreprss_rewb, 
             m_clphy_baseline, m_clphy_total, m_clphy_total_new, 
             m_clphy_advocacy, m_clphy_entry, m_clphy_funding, 
             m_clphy_v2csreprss, 
             m_clphy_baseline_rewb, m_clphy_total_rewb, 
             m_clphy_advocacy_rewb, m_clphy_entry_rewb, m_clphy_funding_rewb, 
             m_clphy_v2csreprss_rewb, 
             m_clpriv_baseline, m_clpriv_total, m_clpriv_total_new, 
             m_clpriv_advocacy, m_clpriv_entry, m_clpriv_funding, 
             m_clpriv_v2csreprss, 
             m_clpriv_baseline_rewb, m_clpriv_total_rewb, 
             m_clpriv_advocacy_rewb, m_clpriv_entry_rewb, m_clpriv_funding_rewb, 
             m_clpriv_v2csreprss_rewb, 
             m_lhr_baseline, m_lhr_total, m_lhr_total_new, 
             m_lhr_advocacy, m_lhr_entry, m_lhr_funding, 
             m_lhr_v2csreprss, 
             m_pts_baseline_train, m_pts_total_train, 
             m_pts_advocacy_train, m_pts_entry_train, m_pts_funding_train, 
             m_pts_v2csreprss_train, 
             m_pts_baseline_rewb_train, m_pts_total_rewb_train, 
             m_pts_advocacy_rewb_train, m_pts_entry_rewb_train, m_pts_funding_rewb_train, 
             m_pts_v2csreprss_rewb_train, 
             m_clphy_baseline_train, m_clphy_total_train, 
             m_clphy_advocacy_train, m_clphy_entry_train, m_clphy_funding_train, 
             m_clphy_v2csreprss_train, 
             m_clphy_baseline_rewb_train, m_clphy_total_rewb_train, 
             m_clphy_advocacy_rewb_train, m_clphy_entry_rewb_train, m_clphy_funding_rewb_train, 
             m_clphy_v2csreprss_rewb_train, 
             m_clpriv_baseline_train, m_clpriv_total_train, 
             m_clpriv_advocacy_train, m_clpriv_entry_train, m_clpriv_funding_train, 
             m_clpriv_v2csreprss_train, 
             m_clpriv_baseline_rewb_train, m_clpriv_total_rewb_train, 
             m_clpriv_advocacy_rewb_train, m_clpriv_entry_rewb_train, m_clpriv_funding_rewb_train, 
             m_clpriv_v2csreprss_rewb_train))
})
```

```{r set-computer-details}
computer <- "Work"

if (computer == "Work") {
  computer_details <- "2019 MacBook Pro with 16 cores and 32 GB of RAM, using Stan through brms through cmdstanr"
} else {
  computer_details <- "2016 MacBook Pro with 4 cores and 16 GB of RAM, using Stan through brms through cmdstanr"
}
```

We ran these models on a `r computer_details`.

@@

### Full data

@@

model_time_e1 <- models_e1 %>% 
  filter(training == "Full data") %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
           `Random effects` = re, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`, `Random effects`)

### Training data

```{r running-time-e1-training}
model_time_e1 <- models_e1 %>% 
  filter(training == "Training") %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
           `Random effects` = re, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`, `Random effects`)

@@

model_time_e2 <- models_e2 %>% 
  filter(training == "Full data") %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
           `Random effects` = re, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`, `Random effects`)

### Training data

```{r running-time-e2-training}
model_time_e2 <- models_e2 %>% 
  filter(training == "Training") %>% 
  mutate(duration = map(actual_model, ~rstan::get_elapsed_time(.$fit)),
         duration = map(duration, ~rownames_to_column(as_tibble(.)))) %>% 
  select(-actual_model) %>% 
  unnest(duration) %>% 
  mutate(model = glue("<code>{model}</code>")) %>% 
  group_by(Model = model, Outcome = outcome_var, `Main predictor` = explan_var, 
           `Random effects` = re, `Family` = family) %>% 
  summarize(`Total time (i.e. longest chain)` = as.duration(max(warmup + sample))) %>%
  ungroup() %>% 
  arrange(Outcome, `Main predictor`, `Random effects`)

@@

- `R/models_pts.R` (for PTS-based models)
- `R/models_clphy.R` (for V-Dem physical violence-based models)
- `R/models_clpriv.R` (for V-Dem private civil liberties-based models)
- `R/models_lhr.R` (for latent human rights-based models)

@@

#### `R/models_lhr.R`

```{r, code=xfun::read_utf8(here::here("R", "models_lhr.R")), eval=FALSE, class.source="fold-hide"}
```

### 2021-04-10 analysis/03_modeling-choices.Rmd
Update analysis notebook to include new laws + latent human rights

Just because the bulk of the relative variation is at at the country level doesn't mean that there isn't significant variability within countries over time. Thus, we should really used a multilevel model because the country-year structure matters *a lot* when explaining human rights abuses

>>>>

Just because the bulk of the relative variation is at at the country level doesn't mean that there isn't significant variability within countries over time. However, the lagged DV seems to soak up pretty much all year-based variability, so we should really use a multilevel model because the country structure matters *a lot* when explaining human rights abuses. There aren't really too many gains in efficiency or predictive power when including `(1 | year)` though.
